### 2017-10-17 paper/sexSelectionSpacingAppendix-ver1.tex
Include spell 4 sex ration and survival graphs in Appendix

% \subsection{Fourth Spell}
% % low education
% \caption*{First three children girls}
% \subfloat[1972--1984 (N=130)]{
%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_r8_pc}}\\
%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_r8_s}} 
% \subfloat[1985--1994 (N=446)]{
%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_r8_pc}}\\
%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_r8_s}}
% \subfloat[1995--2006 (N=200)]{
%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_r8_pc}}\\
%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_r8_s}}
% \caption*{First three children one boy and two girls}
% \subfloat[1972--1984 (N=410)]{
%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_r6_pc}}\\
%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_r6_s}} 
% \subfloat[1985--1994 (N=1,185)]{
%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_r6_pc}}\\
%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_r6_s}}
% \subfloat[1995--2006 (N=601)]{
%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_r6_pc}}\\
%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_r6_s}}
% \label{fig:results_spell4_low_urban}
% \caption*{First three children two boys and one girl}
% \subfloat[1972--1984 (N=389)]{
%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_r4_pc}}\\
%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_r4_s}} 
% \subfloat[1985--1994 (N=1,145)]{
%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_r4_pc}}\\
%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_r4_s}}
% \subfloat[1995--2006 (N=486)]{
%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_r4_pc}}\\
%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_r4_s}}
% \caption*{First three children three boys}
% \subfloat[1972--1984 (N=141)]{
%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_r2_pc}}\\
%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_r2_s}} 
% \subfloat[1985--1994 (N=382)]{
%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_r2_pc}}\\
%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_r2_s}}
% \subfloat[1995--2006 (N=155)]{
%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_r2_pc}}\\
%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_r2_s}}
% % \label{fig:results_spell4_low_urban}
% \caption*{First three children girls}
% \subfloat[1972--1984 (N=752)]{
%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_r7_pc}}\\
%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_r7_s}} 
% \subfloat[1985--1994 (N=1,954)]{
%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_r7_pc}}\\
%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_r7_s}}
% \subfloat[1995--2006 (N=888)]{
%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_r7_pc}}\\
%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_r7_s}}
% \caption*{First three children one boy and two girls}
% \subfloat[1972--1984 (N=2,065)]{
%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_r5_pc}}\\
%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_r5_s}} 
% \subfloat[1985--1994 (N=5,990)]{
%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_r5_pc}}\\
%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_r5_s}}
% \subfloat[1995--2006 (N=2,456)]{
%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_r5_pc}}\\
%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_r5_s}}
% \label{fig:results_spell4_low_rural}
% \caption*{First three children two boys and one girl}
% \subfloat[1972--1984 (N=2,168)]{
%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_r3_pc}}\\
%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_r3_s}} 
% \subfloat[1985--1994 (N=5,439)]{
%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_r3_pc}}\\
%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_r3_s}}
% \subfloat[1995--2006 (N=2,155)]{
%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_r3_pc}}\\
%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_r3_s}}
% \caption*{First three children boys}
% \subfloat[1972--1984 (N=777)]{
%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_r1_pc}}\\
%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_r1_s}} 
% \subfloat[1985--1994 (N=1,895)]{
%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_r1_pc}}\\
%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_r1_s}}
% \subfloat[1995--2006 (N=696)]{
%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_r1_pc}}\\
%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_r1_s}}
% % \label{fig:results_spell4_low_rural}
% \caption*{First three children girls}
% \subfloat[1972--1984 (N=110)]{
%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_r8_pc}}\\
%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_r8_s}} 
% \subfloat[1985--1994 (N=282)]{
%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_r8_pc}}\\
%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_r8_s}}
% \subfloat[1995--2006 (N=144)]{
%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_r8_pc}}\\
%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_r8_s}}
% \caption*{First three children one boy and two girls}
% \subfloat[1972--1984 (N=299)]{
%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_r6_pc}}\\
%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_r6_s}} 
% \subfloat[1985--1994 (N=765)]{
%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_r6_pc}}\\
%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_r6_s}}
% \subfloat[1995--2006 (N=372)]{
%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_r6_pc}}\\
%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_r6_s}}
% \label{fig:results_spell4_med_urban}
% \caption*{First three children two boys and one girl}
% \subfloat[1972--1984 (N=274)]{
%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_r4_pc}}\\
%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_r4_s}} 
% \subfloat[1985--1994 (N=600)]{
%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_r4_pc}}\\
%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_r4_s}}
% \subfloat[1995--2006 (N=275)]{
%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_r4_pc}}\\
%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_r4_s}}
% \caption*{First three children three boys}
% \subfloat[1972--1984 (N=77)]{
%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_r2_pc}}\\
%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_r2_s}} 
% \subfloat[1985--1994 (N=230)]{
%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_r2_pc}}\\
%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_r2_s}}
% \subfloat[1995--2006 (N=90)]{
%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_r2_pc}}\\
%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_r2_s}}
% % \label{fig:results_spell4_med_urban}
% \caption*{First three children girls}
% \subfloat[1972--1984 (N=210)]{
%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_r7_pc}}\\
%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_r7_s}} 
% \subfloat[1985--1994 (N=601)]{
%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_r7_pc}}\\
%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_r7_s}}
% \subfloat[1995--2006 (N=317)]{
%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_r7_pc}}\\
%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_r7_s}}
% \caption*{First three children one boy and two girls}
% \subfloat[1972--1984 (N=581)]{
%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_r5_pc}}\\
%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_r5_s}} 
% \subfloat[1985--1994 (N=1,532)]{
%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_r5_pc}}\\
%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_r5_s}}
% \subfloat[1995--2006 (N=800)]{
%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_r5_pc}}\\
%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_r5_s}}
% \label{fig:results_spell4_med_rural}
% \caption*{First three children two boys and one girl}
% \subfloat[1972--1984 (N=492)]{
%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_r3_pc}}\\
%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_r3_s}} 
% \subfloat[1985--1994 (N=1,197)]{
%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_r3_pc}}\\
%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_r3_s}}
% \subfloat[1995--2006 (N=578)]{
%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_r3_pc}}\\
%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_r3_s}}
% \caption*{First three children three boys}
% \subfloat[1972--1984 (N=158)]{
%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_med_r1_pc}}\\
%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_med_r1_s}} 
% \subfloat[1985--1994 (N=357)]{
%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_med_r1_pc}}\\
%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_med_r1_s}}
% \subfloat[1995--2006 (N=192)]{
%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_med_r1_pc}}\\
%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_med_r1_s}}
% % \label{fig:results_spell4_med_rural}
% \caption*{First three children girls}
% \subfloat[1972--1984 (N=131)]{
%         \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_high_r8_pc}}\\
%         \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_r8_s}} 
% \subfloat[1985--1994 (N=355)]{
%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_high_r8_pc}}\\
%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_r8_s}}
% \subfloat[1995--2006 (N=191)]{
%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_high_r8_pc}}\\
%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_r8_s}}
% \caption*{First three children one boy and two girls}
% \subfloat[1972--1984 (N=353)]{
%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_high_r6_pc}}\\
%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_high_r6_s}} 
% \subfloat[1985--1994 (N=1,062)]{
%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_high_r6_pc}}\\
%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_high_r6_s}}
% \subfloat[1995--2006 (N=590)]{
%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_high_r6_pc}}\\
%         \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_high_r6_s}}
% \label{fig:results_spell4_high_urban}
% \caption*{First three children two boys and one girl}
% \subfloat[1972--1984 (N=309)]{
%         \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_high_r4_pc}}\\

>>>>

\subsection{Fourth Spell}

\begin{figure}[htpb]
\centering
\caption*{First three children girls}
\setcounter{subfigure}{-2}
\subfloat[1972--1984 (N=130)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_urban_ggg_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_urban_ggg_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[1985--1994 (N=446)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_urban_ggg_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_urban_ggg_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{0}
\subfloat[1995--2006 (N=200)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_urban_ggg_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_urban_ggg_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption*{First three children one boy and two girls}
\setcounter{subfigure}{1}
\subfloat[1972--1984 (N=410)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_urban_bgg_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_urban_bgg_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985--1994 (N=1,185)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_urban_bgg_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_urban_bgg_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995--2006 (N=601)]{
    \begin{minipage}{0.26\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_urban_bgg_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_urban_bgg_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from nine months after second birth for urban 
women with no of education by quarter (3 month period). 
Predictions based on age 21 at second birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_spell4_low_urban}
\end{figure}

\begin{figure}[htpb]
\centering
\ContinuedFloat
\caption*{First three children two boys and one girl}
\setcounter{subfigure}{4}
\subfloat[1972--1984 (N=389)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_urban_bbg_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_urban_bbg_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{5}
\subfloat[1985--1994 (N=1,145)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_urban_bbg_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_urban_bbg_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{6}
\subfloat[1995--2006 (N=486)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_urban_bbg_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_urban_bbg_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption*{First three children three boys}
\setcounter{subfigure}{4}
\subfloat[1972--1984 (N=141)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_urban_bbg_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_urban_bbg_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{5}
\subfloat[1985--1994 (N=382)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_urban_bbg_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_urban_bbg_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{6}
\subfloat[1995--2006 (N=155)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_urban_bbg_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_urban_bbg_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
% \label{fig:results_spell4_low_urban}
\caption{(Continued) Predicted probability of having a boy and probability of
no birth yet from nine months after second birth for urban 
women with no of education by quarter (3 month period). 
Predictions based on age 21 at second birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\end{figure}

\begin{figure}[htpb]
\centering
\caption*{First three children girls}
\setcounter{subfigure}{-2}
\subfloat[1972--1984 (N=752)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob.\ boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_rural_ggg_pc}}\\
        \subfloat[Prob.\ no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_rural_ggg_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{-1}
\subfloat[1985--1994 (N=1,954)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_rural_ggg_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_rural_ggg_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{0}
\subfloat[1995--2006 (N=888)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_rural_ggg_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_rural_ggg_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption*{First three children one boy and two girls}
\setcounter{subfigure}{1}
\subfloat[1972--1984 (N=2,065)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_rural_bgg_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_rural_bgg_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{2}
\subfloat[1985--1994 (N=5,990)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_rural_bgg_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_rural_bgg_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{3}
\subfloat[1995--2006 (N=2,456)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_rural_bgg_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_rural_bgg_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{Predicted probability of having a boy and probability of
no birth yet from nine months after second birth for rural
women with no of education by quarter (3 month period). 
Predictions based on age 21 at second birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
\label{fig:results_spell4_low_rural}
\end{figure}

\begin{figure}[htpb]
\ContinuedFloat
\centering
\caption*{First three children two boys and one girl}
\setcounter{subfigure}{4}
\subfloat[1972--1984 (N=2,168)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_rural_bbg_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_rural_bbg_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{5}
\subfloat[1985--1994 (N=5,439)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_rural_bbg_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_rural_bbg_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{6}
\subfloat[1995--2006 (N=2,155)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_rural_bbg_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_rural_bbg_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption*{First three children boys}
\setcounter{subfigure}{4}
\subfloat[1972--1984 (N=777)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g1_low_rural_bbb_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g1_low_rural_bbb_s}} 
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
} 
\setcounter{subfigure}{5}
\subfloat[1985--1994 (N=1,895)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g2_low_rural_bbb_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g2_low_rural_bbb_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\setcounter{subfigure}{6}
\subfloat[1995--2006 (N=696)]{
    \begin{minipage}{0.31\textwidth}
        \captionsetup[subfigure]{labelformat=empty,position=top,captionskip=-1pt,farskip=-0.5pt}
        \subfloat[Prob. boy (\%)]{\includegraphics[width=\textwidth]{spell4_g3_low_rural_bbb_pc}}\\
        \subfloat[Prob. no birth yet]{\includegraphics[width=\textwidth]{spell4_g3_low_rural_bbb_s}}
        \captionsetup[subfigure]{labelformat=parens}
    \end{minipage}
}
\caption{(Continued) Predicted probability of having a boy and probability of
no birth yet from nine months after second birth for rural
women with no of education by quarter (3 month period). 
Predictions based on age 21 at second birth.
Left column shows results prior to sex selection available, middle column before
sex selection illegal and right column after sex selection illegal.
N indicates the number of women in the relevant group in the underlying samples.
}
% \label{fig:results_spell4_low_rural}
\end{figure}
